---
title: "Impressive Client Report"
output:
  html_document:
    theme: spacelab
    highlight: zenburn
---

```{r, echo=FALSE, results="hide", message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(cache=FALSE, eval=TRUE, message=FALSE, warning=FALSE)
files <- list.files(pattern="ex_0.*.shiny.R", full.names=TRUE)
lapply(files, read_chunk)
library(shiny)
```

Using leaflet in R is fairly simple and there are plently of online resources and examples available already.
See the RStudio [tutorial](https://rstudio.github.io/leaflet/) to get started if you haven't already.
Below I present a series of examples which build upon each other.
The code displays both point data and raster data on leaflet maps with Shiny app integration.
The focus here is to show the utility of event observation on the server side for integrating the behavior of browser elements, namely, the leaflet map.

##
##
### Version 0 - Use observers

The app does not do much in this version, but it provides a clear view of how to use observers in Shiny apps to ensure that various inputs and outputs remain mutually well behaved.
Here I use `observeEvent` three distinct times to tie together the reactive behavior of instances of `selectInput` and `leafletOutput`.
The entire `ui.R` at this point is:


```{r}
head(cars)
```

Select a location and click the action button to which the modal is tied. Note how the rest of the app is grayed out when the modal is active.

##
##
### Additional resources

Code for the series of apps shown here can be found on [Github](https://github.com/leonawicz/nwt).
This includes the toy data sets used here so that you can run the app.

See the more advanced [complete app](https://uasnap.shinyapps.io/nwtapp/) on which this example is based.

For another example, see [my first app using leaflet](https://uasnap.shinyapps.io/cc4liteFinal/),
which contains thousands of communities across Alaska and western Canada but which does not use rasterized maps.